Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-15 constantRate/ConstCompFuzzExt-reorg.tex
adding analysis of info theoretic construction

The second construction comes with an additional feature: reusability.  Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.  The enrolled values $w_i$ and $w_j$ are not assumed to be equal, and so information leakage may add up.  Indeed, Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.  Our second construction allows for arbitrary correlation between $w_i$ and $w_j$ against computational adversaries\footnote{Our restriction to computational adversaries implies that the adversary only sees a polynomially bounded number of reuses.  It remains an open problem to construct a polynomially reusable fuzzy extractor against unbounded adversaries.} as long as each marginal $W_i$ is an admissible distribution.  %We do not considering the joint distribution $W_1,..., W_q$.

@@

\noindent Randomness condensers can be built  more efficiently than randomness extractors~(for example~\cite{dodis2013key}).

@@

\subsection{Coding Theory}
\label{sec:coding theory}
We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

\textbf{Notes:}
Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.

@@

\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.  When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).

@@

\section{An information-theoretic construction with $\Huse\le 0$}
\label{sec:info theory cons}
\bnote{needs to be rewritten depending on ordering}
In this section we show an information-theoretic analogue to \consref{cons:first construction}.  %This construction can essentially be seen as replacing the computational point obfuscation with information-theoretic randomness extractors.  
Using this weaker object requires us to make a stronger assumption on our starting distribution.  Furthermore, the important features of \consref{cons:sampling}, $\Huse \le 0$ for a small alphabet and reusability, crucially rely on computational assumptions.  Achieving these benefits information-theoretically is an open question.  We will construct an information-theoretic fuzzy conductor which can be converted to a fuzzy extractor using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).

The main idea of this construction is to first condense entropy from each block of the source and then apply a secure sketch to the extracted information.  Intuitively, we are then able from a large alphabet while paying entropy loss on the smaller alphabet.  %Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).

\begin{construction}
\label{cons:info theoretic}
Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.  We describe $\gen, \rep$ as follows:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $ss \leftarrow \sketch(v_1,..., v_\ell)$.
\item Set $p = (ss, seed_1,..., seed_\ell)$.
\item Output $(v, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\ell))$
\item For $j=1,..., \ell$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $v = \rec(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{definition}
\label{def:partial source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
\end{definition}
\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.  The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).

\begin{lemma}
\label{lem:info theory sec}
Let $\mathcal{W}$ be the family of $(\alpha, \beta)$-partial block sources over $\mathcal{Z}^\ell$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.  Let $(\sketch, \rec)$ be $(\mathcal{Y}^\ell, \tilde{\alpha}(\ell - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).

@@

\subsection{Discussion of Information-Theoretic Construction}
\bnote{write this}

@@

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
%We now return to showing \thref{thm:sampling}.  
In this section we briefly describe why \consref{cons:sampling} is secure.  A proof of security appears \apref{sec:analysis sampling}.  
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

\section{Allowing Correlated Symbols}
In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

@@

\subsection{Discussion of \consref{cons:first construction}}
\label{sec:discussion}
\lnote{I did not check this calculation -- will do}
To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
\[
\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
\]

We consider what entropy is necessary for security.  The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).

@@

\section{Analysis of \consref{cons:info theoretic}}
\begin{proof}[Proof of \lemref{lem:info theory sec}]
Let $W\in \mathcal{W}$.
It suffices to argue correctness and security.  We first argue correctness.  
When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.  Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.  Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.

We now argue security.  Denote by $seed$ the random variable consisting of all $\ell$ seeds and $V$ the entire string of generated $V_1,..., V_\ell$.
Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.  We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\ell)\approx (Y, seed_1,.., seed_\ell)$.  First note since $W$ is $(\alpha, \beta)$-partial block distribution that
there exists a set of indices $J$ where $|J| \geq \ell - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$, 
\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]

@@

\noindent
By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\ell -\beta)$ where 
\[
(\cond(W_\ell, seed_\ell), ..., \cond(W_1, seed_1), seed_\ell,..., seed_1) \approx_{\epsilon\ell} (Z, seed_\ell,...,  seed_1).\]
By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.  %Note that $U_{\mathcal{Y}}^\ell$ is independent of $seed_1,..., seed_\ell$ and so $\Hav(U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p)\ge \tilde{m}$. 
That is, 
\[
(V, seed_1,..., seed_\ell, p) \approx_{\epsilon\ell} (U_{\mathcal{Y}}^\ell, seed_1,..., seed_\ell, p).\]  This completes the proof.
\end{proof}

>>>>

\consref{cons:sampling} comes with an additional feature: reusability.  Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.  The enrolled values $w_i$ and $w_j$ are not assumed to be equal, and so information leakage may add up.  Indeed, Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.  Our second construction allows for arbitrary correlation between $w_i$ and $w_j$ against computational adversaries\footnote{Our restriction to computational adversaries implies that the adversary only sees a polynomially bounded number of reuses.  It remains an open problem to construct a polynomially reusable fuzzy extractor against unbounded adversaries.} as long as each marginal $W_i$ is an admissible distribution.  %We do not considering the joint distribution $W_1,..., W_q$.

@@

\noindent Randomness condensers can be built  more efficiently than randomness extractors~(for example~\cite{dodis2014key}).

@@

@@

\begin{definition}[composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}_{n}$~(resp. $\mathtt{I}_{n+\kappa}$) with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
For notational convenience, when we use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.  When we use digital lockers we denote the oracle provided to the simulator as $I_{w, r}(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points and $r$ is the hidden value~(we will hide the same value in each obfuscation).

@@

\section{Supporting more errors than entropy}
\label{sec:info theory cons}
In this section we show an information-theoretic fuzzy conductor that supports more errors than entropy.
Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
The main idea of this construction is to condense entropy from each block of the source and then apply a secure sketch to the condensed blocks.  The main idea is to correct errors on a large alphabet~(before condensing) while paying for the error correction on a smaller alphabet~(after condensing).%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).

\begin{construction}
\label{cons:info theoretic}
Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $ss \leftarrow \sketch(v_1,..., v_\gamma)$.
\item Set $p = (ss, seed_1,..., seed_\gamma)$.
\item Output $(v, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\gamma))$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $v = \rec(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{definition}
\label{def:partial source}
A distribution $W = W_1,..., W_\gamma$ is an $(\alpha, \beta)$-partial block source if there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
\end{definition}
\defref{def:partial source} is a weakening of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), as only some blocks are required to have entropy conditioned on the past.  The choice of conditioning on the past is arbitrary: a more general sufficient condition is that there exists some ordering of indices where most items have entropy conditioned on all previous items in this ordering~(for example, a ``partial'' reverse block source~\cite{vadhan2003constructing}).  This construction is secure and it supports distributions with more errors than entropy~(proof is in~\apref{sec:info theory sec}).

\begin{lemma}
\label{lem:info theory sec}
Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ wand let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.  Let $(\sketch, \rec)$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).

@@

\subsection{When is $\Huse\le 0$?}

\consref{cons:info theoretic} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.  This means that the input entropy to the secure sketch is $\Theta(\gamma)$.  Standard secure sketches correct a constant fraction of errors at a entropy loss, yielding $\tilde{m} = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\Huse(W) = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma) \log |\mathcal{Z}| <0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with $\Huse\le 0$.  Furthermore, the construction has super-logarithmic output entropy since $\tilde{m} = \Theta(\gamma) = \omega(\log n)$.

@@

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
%We now return to showing \thref{thm:sampling}.  
In this section we briefly describe why \consref{cons:sampling} is secure.  A proof of security appears \apref{sec:analysis sampling}.  
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\subsection{When is $\Huse\le 0$?}
\consref{cons:sampling} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

\section{Allowing Correlated Symbols}
In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Before presenting the construction we provide some definitions from error correcting codes.
We use slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  
}
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

@@

\subsection{When is $\Huse\le 0$?}
\label{sec:discussion}
\lnote{I did not check this calculation -- will do}
In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
We first calculate the size of the Hamming ball.  
\[
\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
\]
The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse (W) = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t\log |\mathcal{Z}|) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then $\Huse\le 0$ and the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\ell)$).

@@

\section{Analysis of \consref{cons:info theoretic}}
\label{sec:info theory sec}
\begin{proof}[Proof of \lemref{lem:info theory sec}]
Let $W\in \mathcal{W}$.
It suffices to argue correctness and security.  We first argue correctness.  
When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.  Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.  Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.

We now argue security.  Denote by $seed$ the random variable consisting of all $\gamma$ seeds and $V$ the entire string of generated $V_1,..., V_\gamma$.
Our goal is to show that $\Hav(V | p)$ is close to a distribution with average min-entropy $\tilde{m}$.  We first argue that there exists a distribution $Y$ where $\Hav(Y | seed)\ge \tilde{\alpha}\beta$ and $(V, seed_1,..., seed_\gamma)\approx (Y, seed_1,.., seed_\gamma)$.  First note since $W$ is $(\alpha, \beta)$-partial block distribution that
there exists a set of indices $J$ where $|J| \geq \gamma - \beta$ such that the following holds:
\[
\forall j\in J, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}) \geq \alpha.
\]
Then consider the first element of $j_1\in J$, $\forall w_1,..., w_{j_1-1}\in W_1,..., W_{j_1-1}$, 
\[\Hoo(W_{j_1} | W_1 = w_1,..., W_{j_1-1} = w_{j_1-1})\ge \alpha.\]

@@

\noindent
By a hybrid argument there exists a distribution $Z$ with $\Hav(Z | seed) \ge \alpha(\gamma -\beta)$ where 
\[
(\cond(W_\gamma, seed_\gamma), ..., \cond(W_1, seed_1), seed_\gamma,..., seed_1) \approx_{\epsilon\gamma} (Z, seed_\gamma,...,  seed_1).\]
By the security of $(\sketch, \rec)$ we know that $\Hav(Z | seed, ss) \ge \tilde{m}$.  %Note that $U_{\mathcal{Y}}^\gamma$ is independent of $seed_1,..., seed_\gamma$ and so $\Hav(U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p)\ge \tilde{m}$. 
That is, 
\[
(V, seed_1,..., seed_\gamma, p) \approx_{\epsilon\gamma} (U_{\mathcal{Y}}^\gamma, seed_1,..., seed_\gamma, p).\]  This completes the proof.
\end{proof}
